Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-21 ms.tex
boxplots and searching energy cost formula
new search in the model

The probability of a male that covers $A_{searched}$ area in time period $dt$ encountering any nest is:
\begin{equation}
    P(\rm {discovery}) = \frac {N \cdot A_{searched}} {A_{total}}
\end{equation}
\citep{Gillespie-1976}
\\
TODO metabolic cost of searching with r and v ?\\

@@

\subsection{Algorithms}
\subsection{Event Algorithms}
So far we are considering two algorithms for stepping through events one is a stochastic simulation algorithm and a simpler (although more compuationally expensive) stepping algorithm.
\subsection{SSA}
Simulating the population dynamics requires accounting for four types of events:

>>>>

The probability of a male that covers $A_{searched}$ area in time period $dt$ encountering any nest is:
\begin{equation}
    P(\rm {discovery}) = \frac {N \cdot A_{searched}} {A_{total}}
\end{equation}
\citep{Gillespie-1976}
The energy used by a male with speed $v$ and radius $r$ is 
\begin{equation}
    E(r,v) = k_{search} \cdot r \cdot v
\end{equation}
where $k_{search}$ is a constant.

@@

\subsection{Algorithms}
\subsection{Event Algorithms}
So far we are considering two algorithms for stepping through events one is a stochastic simulation algorithm and a simpler (although more computationally expensive) naive stepping algorithm.
\subsection{SSA}
Simulating the population dynamics requires accounting for four types of events:
